Worflow

### 2017-06-05 R/workflow.Rmd
update version check

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
knitr::opts_chunk$set(fig.align="center", cache=TRUE, error=FALSE, message=FALSE, warning=TRUE)
#bioconductor:
library(scRNAseq)
library(scone)
library(clusterExperiment)
#github
library(zinbwave)
library(slingshot)
#CRAN
library(ggplot2)
library(gplots)
library(magrittr)
library(matrixStats)
library(Rtsne)
library(RColorBrewer)
library(digest)
library(rARPACK)
set.seed(20)
if(packageVersion("clusterExperiment")<'1.3.0.9005') stop("must have current develop version to avoid bugs")
```

>>>>

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
knitr::opts_chunk$set(fig.align="center", cache=TRUE, error=FALSE, message=FALSE, warning=TRUE)
#bioconductor:
library(scRNAseq)
library(scone)
library(clusterExperiment)
#github
library(zinbwave)
library(slingshot)
#CRAN
library(ggplot2)
library(gplots)
library(magrittr)
library(matrixStats)
library(Rtsne)
library(RColorBrewer)
library(digest)
library(rARPACK)
set.seed(20)
if(packageVersion("clusterExperiment")<'1.3.0.9006') stop("must have current develop version to avoid bugs")
```
